---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# djprtradedata

<!-- badges: start -->
[![R-CMD-check](https://github.com/djpr-data/djprtradedata/workflows/R-CMD-check/badge.svg)](https://github.com/djpr-data/djprtradedata/actions)
[![Codecov test coverage](https://codecov.io/gh/djpr-data/djprtradedata/branch/main/graph/badge.svg)](https://codecov.io/gh/djpr-data/djprtradedata?branch=main)
<!-- badges: end -->

The goal of djprtradedata is to download, tidy and store public data used in the DJPR Trade Dashboard.

## Install djprtradedata

If you do not have the `devtools` package installed, install it from CRAN with: 
```{r, eval = FALSE}
install.packages("devtools")
```

Install `djprtradedata`:
```{r, eval = FALSE}
devtools::install_github("djpr-data/djprtradedata")
```

## Using djprtradedata

Import ABS balance of payments data by State/Territory with `read_bop()`:

```{r}
djprtradedata::read_bop()
```

Import ABS merchandise exports data with `read_merch()`:

```{r}
djprtradedata::read_merch(min_date = as.Date("2021-01-01"),
                          max_date = as.Date("2021-02-01"))
```

Import ABS International Trade Supplementary Information by calendar year with `read_supp_cy()`:

```{r}
djprtradedata::read_supp_cy(3)
```

Import ABS International Trade Supplementary Information by financial year with `read_supp_fy()`:

```{r}
djprtradedata::read_supp_fy(3)
```